\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex

In the above example, \blue{$\star$} (lazy failure) is used in the negative branch
to ensure execution will fail if Bob tries to observe Alice's secret gameboard. To observe
Alice's gameboard, Bob can try to use $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ 
\blue{e_\text{fac}}\code{)}$ form, which takes a label, a key, and a faceted value.
Explicit observation projects a single label $\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ 
to either its positive or negative facet, depending on whether the policy associated 
with $\blue{e_\ell}$ returns true for key $\blue{e_\text{key}}$. If Bob tries to observe 
Alice's board, the policy predicate will return false (from \texttt{(= 1 $\blue{2}$)}) 
and Alice's negative facet $\blue{\star}$ will result.

In other applications, Alice may choose a sensible default value to
reveal to others---she may even want to create a \emph{nested}
facet. For example, a social-networking application may use a
nested facet consisting of two labels for
\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. A user
can then present three views of her social-media profile: \bmth{p_1} to
her family, containing her phone number and other contact information,
\bmth{p_2} to her friends showing her interests, and \bmth{p_3} to
everyone else, showing only her name and email.

@@

Because the applied function can be stateful, faceted execution also
maintains the current privilege level in a \emph{program counter} (PC). The
program counter is a property of the current evaluation context and is used
to build facets when writes are made to the store in a privileged context.
For example, if a stateful function ``splits'' when applied on both the positive and negative
facets of a value faceted by a label $\blue{\ell}$, and on the positive branch
the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
FE semantics will set $x$ to $\facet{\ell}{3}{2}$ so that the value $3$
cannot be leaked from the secure context (speculative execution under the
$\blue{+\ell}$ facet). This is because, for the duration of the app ``split'',
the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
not make this faceting explicit, a sensitive value can leak from one PC to another.
We expand upon these subtleties in Section~\ref{sec:semantics},
where we present a complete semantics for faceted execution.

>>>>

In the above example, \blue{$\star$} (lazy failure) is used in the negative branch
to ensure execution will fail if Bob tries to observe Alice's secret gameboard. To observe
Alice's gameboard, Bob can try to use $\code{(obs}\ \fcol{e_\ell}\ \blue{e_\text{key}}\ 
\blue{e_\text{fac}}\code{)}$ form, which takes a label, a key, and a faceted value.
Explicit observation projects a single label $\fcol{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ 
to either its positive or negative facet, depending on whether the policy associated 
with $\fcol{e_\ell}$ returns true for key $\blue{e_\text{key}}$. If Bob tries to observe 
Alice's board, the policy predicate will return false (from \texttt{(= 1 $\blue{2}$)}) 
and Alice's negative facet $\blue{\star}$ will result.

In other applications, Alice may choose a sensible default value to
reveal to others---she may even want to create a \emph{nested}
facet. For example, a social-networking application may use a
nested facet consisting of two labels for
\rmth{\ell_{\text{Friends}}} and \rmth{\ell_{\text{Family}}}. A user
can then present three views of her social-media profile: \bmth{p_1} to
her family, containing her phone number and other contact information,
\bmth{p_2} to her friends showing her interests, and \bmth{p_3} to
everyone else, showing only her name and email.

@@

Because the applied function can be stateful, faceted execution also
maintains the current privilege level in a \emph{program counter} (PC). The
program counter is a property of the current evaluation context and is used
to build facets when writes are made to the store in a privileged context.
For example, if a stateful function ``splits'' when applied on both the positive and negative
facets of a value faceted by a label $\fcol{\ell}$, and on the positive branch
the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
FE semantics will set $x$ to $\facet{\ell}{3}{2}$ so that the value $3$
cannot be leaked from the secure context (speculative execution under the
\rmth{+\ell} facet). This is because, for the duration of the app ``split'',
the evaluation context records that all values are implicitly guarded by \rmth{+\ell}
and then \rmth{-\ell}, respectively. If the semantics for $\texttt{set!}$ does
not make this faceting explicit, a sensitive value can leak from one PC to another.
We expand upon these subtleties in Section~\ref{sec:semantics},
where we present a complete semantics for faceted execution.
